### 2025-06-12 acronyms/acronyms.tex
colleges
bpc
CBS
acronyms
alt futures
eoi
acse

@@

@@

@@

@@

@@

@@

\newacronym{cbs}{CBS}{Consent-Based Siting}

@@

@@

@@

@@

@@

@@

@@

>>>>

\newacronym{cei}{CEI}{College of Eastern Idaho}

@@

\newacronym{cos}{CSI}{College of Southern Idaho}
\newacronym{cwi}{CWI}{College of Western Idaho}
\newacronym{noc}{NIC}{North Idaho College}

@@

\newacronym{um}{UM}{University of Michigan}

@@

\newacronym{csn}{CSNR}{Center for Space Nuclear Research}

@@

\newacronym{asc}{ASCE}{American Society of Civil Engineers}

@@

\newacronym{dhs}{DHS}{Department of Homeland Security}

@@

\newacronym{cbs}{CBS}{Collaborative-Based Siting}
%\newacronym{cbs}{CBS}{Consent-Based Siting}

@@

\newacronym{msr}{MSR}{Molten Salt Reactor}

@@

\newacronym{snm}{SNM}{Special Nuclear Material}

@@

\newacronym{hri}{HRI}{Human Risk Index}

@@

\newacronym{nrx}{NRI}{National Risk Index}

@@

\newacronym{afs}{AF}{Alternative Future}

@@

\newacronym{caa}{CAA}{Consolidated Appropriations Act}

@@

\newacronym{eoi}{EoI}{Expression of Interest}
